### 2016-07-29 mcmc.tex
nope

\noindent
David~W.~Hogg\\
\affil{Simons~Center~for~Data~Analysis,
       Simons~Foundation}\\
\affil{Center~for~Cosmology~and~Particle~Physics, Department~of~Physics,
       New~York~University}\\
\affil{Center~for~Data~Science,
       New~York~University}\\
\affil{Max-Planck-Institut~f\"ur~Astronomie, Heidelberg}\\[1ex]
Daniel~Foreman-Mackey\\
\affil{Sagan Fellow}\\
\affil{Department~of~Astronomy, University~of~Washington}

@@

\begin{problem}\label{prob:fittingaline}
DFM: do this problem.
For a real-world inference problem, read enough of
\citet{fittingaline} to understand and execute Exercise~6 in that
document.
\end{problem}

>>>>

\noindent
\textbf{David~W.~Hogg}\\
\affil{Simons~Center~for~Data~Analysis,
       Simons~Foundation}\\
\affil{Center~for~Cosmology~and~Particle~Physics, Department~of~Physics,
       New~York~University}\\
\affil{Center~for~Data~Science,
       New~York~University}\\
\affil{Max-Planck-Institut~f\"ur~Astronomie, Heidelberg}\\[1ex]
\textbf{Daniel~Foreman-Mackey}\\
\affil{Sagan Fellow}\\
\affil{Department~of~Astronomy, University~of~Washington}

@@

\begin{problem}\label{prob:fittingaline}
For a real-world inference problem, read enough of
\citet{fittingaline} to understand and execute Exercise~6 in that
document.
\end{problem}
